---
title: "Association_Rules"
author: "SeuljiMoon"
date: "2023-08-18"
output: 
  html_document: 
    toc: yes
---

연관관계 분석을 위한 package 설치

```{r echo=T , message=F}
if(!require("arules")) install.packages("arules")
if(!require("arulesViz")) install.packages("arules")
if(!require("visNetwork")) install.packages("visNetwork")
if(!require("igraph")) install.packages("igraph")
```

library setup
```{r}
library(arules)
library(arulesViz)
library(visNetwork)
library(igraph) 
library(data.table); library(dplyr)
```

Read dataset
```{r}
setwd("C:/Users/cmc/Documents/GitHub/NHIS_AssociationRules")
wide_raw <- fread("data/0710_como_network_out.csv")

head(wide_raw)
```

Split dataset
comorbidities status 2-years after multiple myeloma diagnosis

```{r}
sm.names<-c("mi_yes", "pvd_yes", "cd_yes", "dem_yes", "hp_yes"
            ,"im_yes", "cpd_yes", "chf_yes", "pud_yes", "mld_yes"
            , "rd_yes", "dia_yes", "cancer_yes", "aids_yes")

cci.names <- c("MI", "PVD", "CVD", "Dementia", "Plegia", "IM",
               "CPD", "CHF", "PUD", "Liver",
               "RD","Diabetes", "Cancer", "AIDS")

wide_raw_after <- wide_raw %>% select(INDI_DSCM_NO, c90_yn, sex,
                                      age, ageg4, insu_g2
                                      , paste0(sm.names)
                                      , death, surv_years)
```

change colnames
```{r}
colnames(wide_raw_after) <- c("ID","c90_yn","sex","age", "ageg4", "insu_g2",
                              cci.names,
                              "death", "surv_years")
```

dataframe 을 transaction type으로 변환

1. Multiple myeloma 환자에 대해서만 분석
```{r}
a <- wide_raw_after |> filter(c90_yn==1)
trans <- a
row.id <- a[ , 1]
trans <- a[, c(7:20)]
trans <- as.data.frame(sapply(trans,as.logical)) 

transdf <- as(trans, "transactions")

transdf
summary(transdf)
```
check top comorbidities frequency using histogram
```{r}
itemFrequencyPlot(transdf,
                  type="relative",
                  topN=10, # can be changed to the number of interest
                  horiz=TRUE,
                  col='pink',
                  xlab='',
                  main='CCI frequency, relative')


itemFrequencyPlot(transdf,
                  type="absolute",
                  topN=14,
                  horiz=TRUE,
                  col='pink',
                  xlab='',
                  main='CCI frequency, absolute')
```

make simple contingency table 
```{r}
tbl <- crossTable(transdf)
tbl <- crossTable(transdf, sort=TRUE)

crossTable(transdf, measure='lift',sort=T)

```

Association rules modeling

search for rules : support, confidence 적절한 threshold 설정
```{r}
rules <- apriori(transdf,
                 parameter = list(support=.0006,
                                  confidence=.50,
                                  #minlen=2,
                                  target='rules' # to mine for rules
                 ))

summary(rules)
```
총 350개의 rule 확인 가능
```{r}
quality(rules)$chi <- interestMeasure(rules, measure='chi', significance=T, transdf)
inspect(sort(rules, by='lift', decreasing = T)[1:40])
```

Network plot 시각화
```{r}
## 시각화
plot(rules, method="graph", control=list(type="items") )
plot(rules, method = "grouped")
```

